### 2014-11-12 tex/intro.tex
still working on the intro
intro moving along

In this work, we present a technique for heap summarization,
initialization, and analysis in the context of symbolic execution. We
represent the heap as a bipartiate graph of references and sets of
constraints over locations. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of
objects, allowing us to handle aliasing and (ii) it does not require
rewrite of the constraints during updates to the heap. We lazily
initialize, summarize, and update the bipartiate graph during symbolic
execution. Unlike GSE, however, we only partition the heaps at points
of divergence in the control flow graph. These points of
non-determinism at field accesses that lead to null-pointer exception
and checking equality of references. The former represents a
divergence due to exceptional control flow while the later due to
program structure.

>>>>

In this work, we present a technique for heap summarization,
initialization, and analysis in the context of symbolic execution. We
represent the heap as a bipartiate graph of references and sets of
constraints over locations. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of
objects, allowing us to handle aliasing and (ii) it does not require
rewrite of the constraints during updates to the heap nor does it
introduce any auxillary variables in the constraints. During symbolic
execution, we initialize, summarize, and update the bipartiate
graph. Unlike GSE, however, the heaps are partitioned only at points
of divergence in the control flow graph. These points of
non-determinism are at field accesses that lead to null-pointer
exceptions and at comparisons of references. The former represents a
divergence due to exceptional control flow while the later due to
program structure.
